Contextuality and Nonlocality in Discrete Quantum Theory

### 2015-11-22 DQC3.tex
Replace \ComplexI by \rmi because of IOPLaTeXGuidelines
Add the date to title page, and fix some obverious bugs...

\newcommand{\ComplexI}{\text{i}}
\newcommand{\fnorm}[1]{\mathsf{N}(#1)}
\newcommand{\mod}{\mbox{mod }}

@@

\title{Contextuality and Nonlocality in \\ Discrete Quantum Theory}

@@

\ead{ortizg@indiana.edu}

@@

@@

The dimension of an eigenspace may be less than the multiplicity of
its eigenvalue. For example, consider a Hermitian matrix 

@@

The only eigenspace of $\mathbf{H}_{2}$ is spanned by $\begin{pmatrix}1\\
-1+\rmi
\end{pmatrix}$. The dimension of eigenspace is 1 less than 2 so that $\mathbf{H}_{2}$

@@

$1$ with the post-measurement state $\begin{pmatrix}1\\
-1+\rmi
\end{pmatrix}$. However, only operator always producing $1$ is the identity operator

@@

-1+\rmi & 1-

@@

are $-1-\rmi$ with $\begin{pmatrix}1\\
-1-\rmi
\end{pmatrix}$ and $-1+\rmi$ with $\begin{pmatrix}1\\
1+\rmi
\end{pmatrix}$. It is easy to verify the eigenvalues are not in $\ff{3}$, and the

@@

preserved when we map them into finite fields.

>>>>

\newcommand{\fnorm}[1]{\mathsf{N}(#1)}
\newcommand{\mod}{\mbox{mod }}

@@

\title{Contextuality and Nonlocality in Discrete Quantum Theory}

@@

\ead{ortizg@indiana.edu}
\begin{abstract}
\today
\end{abstract}

@@

\noindent{\it Keywords\/}: {contextuality, nonlocality, measurement process, Gleason's theorem,
Bell's theorem, the Kochen-Specker theorem}

@@

 The dimension of an eigenspace may be less than the multiplicity
of its eigenvalue. For example, consider a Hermitian matrix 

@@

The only eigenspace of $\mathbf{H}_{2}$ is spanned by $\left(\begin{array}{cc}
1 & -1+\rmi\end{array}\right)^{T}$. The dimension of eigenspace is 1 less than 2 so that $\mathbf{H}_{2}$

@@

$1$ with the post-measurement state $\left(\begin{array}{cc}
1 & -1+\rmi\end{array}\right)^{T}$. However, only operator always producing $1$ is the identity operator

@@

-1+\rmi & -1

@@

are $-1-\rmi$ with $\left(\begin{array}{cc}
1 & -1-\rmi\end{array}\right)^{T}$ and $-1+\rmi$ with $\left(\begin{array}{cc}
1 & 1+\rmi\end{array}\right)^{T}$. It is easy to verify the eigenvalues are not in $\ff{3}$, and the

@@

preserved when we map them into finite fields. \yutsung{Although
may not need to type it down, need to check the definition of the
map, passing congruence into square root, and partial homomorphism...
etc.}
